MPhil

### 2024-05-13 meetings/07-05-2024_slides.qmd
improve monitoring

Found the source for the spikes and fixed it: `.generate()` is the wrong method, need `.forward()` $\to$ wrong conditionals! Now maximizes the likelihood and faster!

- New generated slogans seem better, space looks more interesting (have yet to do the "box" normalization)
- Maybe even further performance gains by using `past_key_values`

@@

@@

- [ ] SLURM application
- [ ] Set appointment for pre-defense
- [ ] Find third assessor 
- [ ] Complete data management survey

>>>>

Improved the optimization: `.generate()` is the wrong method, need `.forward()` $\to$ wrong conditionals! Now maximizes the likelihood and is faster!

- Space looks different now; Does maximizing the likelihood collapse the encoding space?
- Maybe even further performance gains by using `past_key_values`?

@@

MPhil: Need to start working towards the paper now

---

@@

- [ ] There seem to be issues with the access to the data for me now
- [ ] SLURM application
- [ ] Set appointment for pre-defense
- [ ] Find third assessor
- [ ] Complete data management survey

---

![Maxmimum Likelihood (nLL)](./figures/07-05-24-04.png)

---

![Encoded data points](./figures/07-05-24-03.png)

---

![Exploring the encoding space with generation, x are candidates](./figures/07-05-24-01.png)

---

![Cosine similarity between the candidate points](./figures/07-05-24-02.png)

### 2024-05-13 writing/paper.qmd
improve monitoring

@@

@@

<!-- TODO: Consider renaming this headline -->
# Theory

@@

The Autoencoder $\operatorname{AE}_{\Beta} \left(\cdot \right): \lbrace 0, 1 \rbrace^{C} \to \mathbb{R}^E$, with parameters $\Beta$

@@

@@

@@

- Optimization
  - Computation time, scaling
- Encoding space
  - example tangible, intangible
  - generations from encoding space
  - Wasteland, geometrical shape and where it comes from
- Application to CBC data

@@

- Generative AI for personalization

@@

>>>>

---
author: Finn-Ole Höner (657110)
title: "MPhil"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 20mm
            - bottom = 20mm
            - left = 20mm
            - right = 20mm
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

- What is missing from preference learning? How is this different?
  - Media products / things are different from products as attribute bundles
    - We can directly represent the product itself?
  - Brands and their role in advertising

@@

<!-- TODO: Consider renaming this headline -->

# Theory

@@

The Autoencoder $\operatorname{AE}_{\mathcal{B}} \left(\cdot \right): \lbrace 0, 1 \rbrace^{C} \to \mathbb{R}^E$, with parameters $\mathcal{B}$

@@

- Adding covariates to the AE

- LLM judge to rate claims

@@

- Different generation strategies, use beam search to get closer to max LL

@@

- Optimization
  - Computation time, scaling
- Encoding space
  - example tangible, intangible
  - generations from encoding space
  - Wasteland, geometrical shape and where it comes from
- Measures of fit
  - areas in the encoding space (count out the pixels and compare to curvature of LL?)
  - analysis of the trees
  - Gap between most likely and second most likely token
- Application to MR data

- Comparison to BERT embeddings

@@

- Generative AI for personalization
- Brands
- Wording

@@

- Comparison to BERT embeddings
